Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-25 paper/aldebaran.tex
deleting duplicate bib entries

\section{Asteroseismology of Red Giants}
Asteroseismology is a powerful tool for the charaterisation of red giant stars \citep[see][for a detailed review]{2013ARA&A..51..353C}.  Red giants are solar-type pulsators, they exhibit acoustic modes of oscillation that are both excited and damped by stellar convection.  In the frequency-power spectrum of either radial velocity of photometric observations, these modes of oscillation form an often intricate pattern of sharp peaks where the properties of the pattern can be mapped back to intrinsic stellar properties \citep[e.g.,][]{2016AN....337..774D}.  The easiest properties of the pattern to determine are the the frequency of maximum amplitude \numax and the so-called large separation \Dnu \citep{1995A&A...293...87K}.  The two observables are often referred to as the global average seismic parameters.

>>>>

\section{Asteroseismology of Red Giants}
Asteroseismology is a powerful tool for the charaterisation of red giant stars \citep[see][for a detailed review]{2013ARA&A..51..353C}.  Red giants are solar-type pulsators, they exhibit acoustic modes of oscillation that are both excited and damped by stellar convection.  In the frequency-power spectrum of either radial velocity of photometric observations, these modes of oscillation form an often intricate pattern of sharp peaks where the properties of the pattern can be mapped back to intrinsic stellar properties \citep[e.g.,][]{2016AN....337..774D}.  The easiest properties of the pattern to determine are the the frequency of maximum amplitude \numax and the so-called large separation \Dnu \citep{Kjeldsen1995}.  The two observables are often referred to as the global average seismic parameters.
